Galois Transformers and Modular Abstract Interpreters

### 2015-03-26 writeup/oopsla2015.tex
almost down to 14 pages.
almost done
Small typo in abstract.

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{stmaryrd}
\usepackage{galois}
\usepackage{float}
\usepackage{latexsym}
\usepackage{balance}
\usepackage{array}
\usepackage{tikz}
\usetikzlibrary{matrix}
\floatstyle{boxed}
\restylefloat{figure}
\usepackage[font=small,skip=0pt]{caption}

@@

% These are supposed to make align* not have breaks around it...
\setlength{\abovedisplayskip}{0em}
\setlength{\belowdisplayskip}{0em}
\setlength{\abovedisplayshortskip}{0em}
\setlength{\belowdisplayshortskip}{0em}

@@

We solve the problem of systematically constructing static analyzers by
introducing \emph{Galois transformers}: monad transformers that
transports Galois connection properties.  In concert with a monadic
interpreter, we define a library of monad transformers that
implement building blocks for classic analysis parameters like context, path,
and heap (in)sensitivity. Moreover, these can be composed together 
% to realize a program analysis monad, 
\emph{independent of the language being analyzed}.

>>>>

\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{bm}
\usepackage{stmaryrd}
\usepackage{galois}
\usepackage{float}
\usepackage{latexsym}
\usepackage{balance}
\usepackage{array}
\usepackage{tikz}
\usepackage{etoolbox}
\usetikzlibrary{matrix}
\floatstyle{boxed}
\restylefloat{figure}
\usepackage[font=small,skip=0pt]{caption}

@@

% These make align* have smaller breaks around it. -DCD
\newcommand{\zerodisplayskips}{%
  \setlength{\abovedisplayskip}{4pt}
  \setlength{\belowdisplayskip}{4pt}
  \setlength{\abovedisplayshortskip}{0pt}
  \setlength{\belowdisplayshortskip}{0pt}}
% \appto{\normalsize}{\zerodisplayskips}
\appto{\small}{\zerodisplayskips}

% This makes floats have less space between them and text.
\setlength{\textfloatsep}{8pt}

@@

We solve the problem of systematically constructing static analyzers by
introducing \emph{Galois transformers}: monad transformers that
transport Galois connection properties.  In concert with a monadic
interpreter, we define a library of monad transformers that
implement building blocks for classic analysis parameters like context, path,
and heap (in)sensitivity. Moreover, these can be composed together 
% to realize a program analysis monad, 
\emph{independent of the language being analyzed}.
